DRAFT

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

### • Country
### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
```{r echo=FALSE}
kable(count(df2, country) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```
```{r echo=FALSE}
data <- data.frame(
  class=c('comfort', 'first class', 'luxury', 'standard', 'tourist'),
  value=c(17695, 14154, 2307, 4025, 877)
)
data <- data %>% 
  arrange(desc(class)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

@@

## 1.3 Findings
### • Mean prices for countries
```{r echo=FALSE}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

### • Country
### The countries with the most records are Italy and Germany. Together they make up 66% of all records.
```{r}
kable(count(df2, country) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

```{r echo=FALSE}
data <- data.frame(
  class=c('comfort', 'first class', 'luxury', 'standard', 'tourist'),
  value=c(17695, 14154, 2307, 4025, 877)
)
data <- data %>% 
  arrange(desc(class)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

@@

## 1.3 Findings
### • Mean prices for countries

```{r echo=FALSE}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
  kableExtra::kable_styling(latex_options = "hold_position")
```
